Developing a Bubble Chamber Particle Discriminator Using Semi-Supervised Learning

### 2018-11-27 documentation/paper.tex
Added more authors and email
Final changes

\usepackage[margin=1in]{geometry}
\usepackage{textcomp}
\usepackage{parskip}
\usepackage{amsmath}
\usepackage{authblk}
\usepackage[backend=biber, style=alphabetic, sorting=ynt]{biblatex}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{caption}
\usepackage{hyperref}
\usepackage{lineno}

\DeclareUnicodeCharacter{0301}{'}

\linenumbers

@@

Superheated fluid detectors have an intrinsic insensitivity to the relatively diffuse energy depositions from electron recoils \cite{pico}, and neutron backgrounds are mitigated by shielding the detector volume in a 20 t water tank. Alpha decays along the U/Th chains present the dominant remaining background which must be distinguished from nuclear recoils acoustically \cite{isotopes}.

@@

\begin{enumerate}
    \item This was a highly effective configuration, producing 96\% accuracy and a class-wise standard deviation dramatically better than the original PICO-60 neural network on that data set.
    \item The use of the exact same input format as AP makes the algorithms more directly comparable.
    \item If position correction is not applied, there is some risk of introducing a bias to the network's training data because of the different position distributions of the two classes.
\end{enumerate}

@@

>>>>

\usepackage[margin=1in]{geometry}
\usepackage{textcomp}
\usepackage{parskip}
\usepackage{amsmath}
\usepackage{authblk}
\usepackage[backend=biber, style=alphabetic, sorting=ynt]{biblatex}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{caption}
\usepackage{hyperref}

@@

Superheated fluid detectors have an intrinsic insensitivity to the relatively diffuse energy depositions from electron recoils \cite{pico}, and neutron backgrounds are mitigated by shielding the detector volume in a 20~t water tank. Alpha decays along the U/Th chains present the dominant remaining background which must be distinguished from nuclear recoils acoustically \cite{isotopes}.

@@

\begin{enumerate}
    \item This was a highly effective configuration, producing 96\% accuracy and a class-wise standard deviation dramatically better than the original PICO-60 neural network on that data set.
    \item The use of the exact same input format as AP makes the algorithms more directly comparable.
    \item If position correction is not applied, there is some risk of introducing a bias to the network's training data because there are different position distributions of the two classes; neutron events during calibration runs occur more frequently near the wall of the detector where the calibration source is placed.

    Note that it is possible some this bias leaks through to some degree if position corrections are not perfect; acoustics may be noticeably different near the walls of the vessel in particular.
\end{enumerate}

@@

Implementation code for all algorithms discussed in this paper can be found at \url{https://github.com/brendon-ai/dark-matter}.
